Local to global N input modelling

### 2025-06-09 manuscript.qmd
Updates to display feeds better

feed_pal <- c("past" = brewer.pal(9, "Set1")[1], "reference" = brewer.pal(9, "Set1")[2], "future" = brewer.pal(9, "Set1")[3])
cohort_pal <- c("1" = brewer.pal(9, "Set1")[1], "2" = brewer.pal(9, "Set1")[2], "3" = brewer.pal(9, "Set1")[3], "all" = "black")
```

@@

inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
  CAN1 = c(-132, -122, 47.75, 54.25),
  CAN2 = c(-70, -54, 43, 48.5),
  EUR = c(-26, 30, 51, 71),
  CHI = c(-77.5, -62.5, -56, -25),
  AUS = c(144, 149.5, -39.75, -44)
)
labels_spec <- c(CAN1 = "bottom_left_outside", CAN2 = "bottom_right_outside", EUR = "bottom_left_outside", CHI = "top_left_outside", AUS = "bottom_left_outside")
labels_offset <- c(CAN1 = 1, CAN2 = 2, EUR = 1.75, CHI = 1.75, AUS = 3.5)

@@

```{r patchwork-map-mercator}
#| fig-cap: |
#|   Possibly use a patchwork map to show spatial results?
#| fig-height: 9
#| fig-width: 9.5

@@

inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
  CAN1 = c(-132, -122, 48.5, 54),
  CAN2 = c(-70, -54, 43, 48.5),
  EUR = c(-23, 28.5, 52, 71),
  CHI = c(-78, -62, -55.5, -27),
  AUS = c(144, 149, -40.75, -43.75)
)

@@

p_Aus <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["AUS"]][1:2], ylim = inset_boxes_sm[["AUS"]][3:4])  +
  draw_label("E", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["AUS"]][1], y = inset_boxes_sm[["AUS"]][3], 
             hjust = 0, vjust = 1)
p_Eur <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["EUR"]][1:2], ylim = inset_boxes_sm[["EUR"]][3:4]) +
  draw_label("C", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["EUR"]][1], y = inset_boxes_sm[["EUR"]][4], 
             hjust = -1, vjust = 1)
p_Chi <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CHI"]][1:2], ylim = inset_boxes_sm[["CHI"]][3:4]) +
  theme(legend.position = "right") +
  draw_label("D", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CHI"]][1], y = inset_boxes_sm[["CHI"]][4], 
             hjust = 0, vjust = 0)
p_Can1 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN1"]][1:2], ylim = inset_boxes_sm[["CAN1"]][3:4]) +
  draw_label("A", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN1"]][1], y = inset_boxes_sm[["CAN1"]][4], 
             hjust = -1, vjust = 0)
p_Can2 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN2"]][1:2], ylim = inset_boxes_sm[["CAN2"]][3:4]) +
  draw_label("B", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN2"]][1], y = inset_boxes_sm[["CAN2"]][4], 
             hjust = 0, vjust = 1)

@@

df <- feed_params[["reference"]]
contribP_1 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
tP_1 <- sum(contribP_1)
digestP_1 <- sum(df[["Proteins"]]$digest * contribP_1)/tP_1

contribL_1 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_1 <- sum(contribL_1)
digestL_1 <- sum(df[["Lipids"]]$digest * contribL_1)/tL_1

contribC_1 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
tC_1 <- sum(contribC_1)
digestC_1 <- sum(df[["Carbohydrates"]]$digest * contribC_1)/tC_1

df <- feed_params[["past"]]
contribP_2 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
tP_2 <- sum(contribP_2)
digestP_2 <- sum(df[["Proteins"]]$digest * contribP_2)/tP_2

contribL_2 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_2 <- sum(contribL_2)
digestL_2 <- sum(df[["Lipids"]]$digest * contribL_2)/tL_2

contribC_2 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
tC_2 <- sum(contribC_2)
digestC_2 <- sum(df[["Carbohydrates"]]$digest * contribC_2)/tC_2

df <- feed_params[["future"]]
contribP_3 <- df[["Proteins"]]$proportion*df[["Proteins"]]$macro
tP_3 <- sum(contribP_3)
digestP_3 <- sum(df[["Proteins"]]$digest * contribP_3)/tP_3

contribL_3 <- df[["Lipids"]]$proportion*df[["Lipids"]]$macro
tL_3 <- sum(contribL_3)
digestL_3 <- sum(df[["Lipids"]]$digest * contribL_3)/tL_3

contribC_3 <- df[["Carbohydrates"]]$proportion*df[["Carbohydrates"]]$macro
tC_3 <- sum(contribC_3)
digestC_3 <- sum(df[["Carbohydrates"]]$digest * contribC_3)/tC_3
```

@@

* Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].
* The reference feed is `r round(100*tP_1,1)`% protein, `r round(100*tL_1,1)`% lipid, `r round(100*tC_1,1)`% carbohydrate. 
* The past feed is `r round(100*tP_2,1)`% protein, `r round(100*tL_2,1)`% lipid, `r round(100*tC_2,1)`% carbohydrate. 
* The future feed is `r round(100*tP_3,1)`% protein, `r round(100*tL_3,1)`% lipid, `r round(100*tC_3,1)`% carbohydrate. 
* Within the reference feed, protein is overall `r round(100*digestP_1,1)`% digestible, lipid is overall `r round(100*digestL_1,1)`% digestible, and carbohydrate is overall `r round(100*digestC_1,1)`% digestible.
* Within the past feed, protein is overall `r round(100*digestP_2,1)`% digestible, lipid is overall `r round(100*digestL_2,1)`% digestible, and carbohydrate is overall `r round(100*digestC_2,1)`% digestible.
* Within the future feed, protein is overall `r round(100*digestP_3,1)`% digestible, lipid is overall `r round(100*digestL_3,1)`% digestible, and carbohydrate is overall `r round(100*digestC_3,1)`% digestible.

@@

@@

```{r weight and biomass data}
farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
  list.files(full.names = T)

# qs::qread(farmrun_files[1]) %>% names()
weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>% bind_rows()
biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>% bind_rows()
```

@@

uneaten_total <- farmrun_files %>% 
  purrr::map(function(f) {qs::qread(f)[["total_uneat_stat"]]}) %>% 
  bind_rows() %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  rename(uneat_mean = mean.x, biomass_mean = mean.y,
         uneat_sd = sd.x, biomass_sd = sd.y) %>% 
  mutate(uneat_sd = uneat_sd/uneat_mean,
         biomass_sd = biomass_sd/biomass_mean,
         uneat_biom_mean = uneat_mean/biomass_mean,
         uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)

uneaten_total_stats <- uneaten_total %>% 
  group_by(feed, farm_ID) %>% 
  reframe(total = sum(uneat_biom_mean)) %>% 
  group_by(feed) %>% 
  reframe(min = minna(total),
          max = maxna(total),
          mean = meanna(total)) %>% 
  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
  mutate(min = round(min,2),
         max = round(max,2),
         mean = round(mean,2))
```

* Total reference uneaten feed across a cohort (548 days) ranged from `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$, with a mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]`.
* There was very little difference between the past and future feeds and the reference feed. Uneaten past feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]`) while uneaten future feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`).
* @fig-total-uneaten-perday shows the range of total uneaten feed per day across countries.

>>>>

feed_pal <- c("past" = "#E41A1C", "reference" = "#377EB8", "future" = "#4DAF4A")  
cohort_pal <- c("1" = "#E41A1C", "2" = "#377EB8", "3" = "#4DAF4A", "all" = "black")
macro_pal <- c(
  "protein" = "darkred", "P" = "darkred", 
  "carbohydrates" = "steelblue", "C" = "steelblue", 
  "lipids" = "darkgoldenrod1", "L" = "darkgoldenrod1"
)
```

@@

inset_boxes <- list(   # lonmin, lonmax, latmin, latmax
  CAN1 = c(-132, -122, 47.75, 54.25),
  CAN2 = c(-70, -54, 43, 48.5),
  EUR = c(-26, 30, 51, 72),
  CHI = c(-77.5, -62.5, -56, -25),
  AUS = c(144, 149.5, -44, -39.75)
)
labels_spec <- c(CAN1 = "bottom_left_outside", CAN2 = "bottom_right_outside", EUR = "bottom_left_outside", CHI = "top_left_outside", AUS = "bottom_left_outside")
labels_offset <- c(CAN1 = 1, CAN2 = 2, EUR = 1.75, CHI = 1.75, AUS = 3.5)

@@

```{r patchwork-map-mercator}
#| fig-cap: |
#|   Example of a patchwork
#| fig-height: 9
#| fig-width: 9.5

@@

inset_boxes_sm <- list(   # lonmin, lonmax, latmin, latmax
  CAN1 = c(-132, -122, 48.5, 54),
  CAN2 = c(-70, -54, 43, 48.5),
  EUR = c(-23, 28.5, 52, 71),
  CHI = c(-78, -62, -55.5, -27),
  AUS = c(144, 149, -43.75, -40.75)
)

inset_boxes_sm <- map(inset_boxes_sm, function(bx) {
  list(
    xlims = bx[1:2],
    ylims = bx[3:4],
    labx = bx[1],
    laby = bx[4]
    )
})

@@

p_Can1 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN1"]][["xlims"]], 
           ylim = inset_boxes_sm[["CAN1"]][["ylims"]])  +
  draw_label("A", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN1"]][["labx"]], 
             y = inset_boxes_sm[["CAN1"]][["laby"]], 
             hjust = -1, vjust = 0.5)
p_Can2 <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CAN2"]][["xlims"]], 
           ylim = inset_boxes_sm[["CAN2"]][["ylims"]])  +
  draw_label("B", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CAN2"]][["labx"]], 
             y = inset_boxes_sm[["CAN2"]][["laby"]], 
             hjust = 0.5, vjust = 0)
p_Eur <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["EUR"]][["xlims"]], 
           ylim = inset_boxes_sm[["EUR"]][["ylims"]])  +
  draw_label("C", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["EUR"]][["labx"]], 
             y = inset_boxes_sm[["EUR"]][["laby"]], 
             hjust = -1, vjust = 0.5)
p_Chi <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["CHI"]][["xlims"]], 
           ylim = inset_boxes_sm[["CHI"]][["ylims"]])  +
  theme(legend.position = "right") +
  draw_label("D", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["CHI"]][["labx"]], 
             y = inset_boxes_sm[["CHI"]][["laby"]], 
             hjust = 0, vjust = 0)
p_Aus <- p1 + 
  coord_sf(xlim = inset_boxes_sm[["AUS"]][["xlims"]], 
           ylim = inset_boxes_sm[["AUS"]][["ylims"]])  +
  draw_label("E", size = 14, fontface = "bold", 
             x = inset_boxes_sm[["AUS"]][["labx"]], 
             y = inset_boxes_sm[["AUS"]][["laby"]], 
             hjust = 0, vjust = 0)

@@

feed_summary <- map_dfr(names(feed_params), function(feed) {
  df <- feed_params[[feed]]
  map_dfr(c("Proteins", "Lipids", "Carbohydrates"), function(macro) {
    contrib <- df[[macro]]$proportion * df[[macro]]$macro
    total <- sum(contrib)
    digest <- sum(df[[macro]]$digest * contrib) / total
        tibble(
      feed = feed,
      macro = macro,
      total = total,
      digest = digest
    )
  })
}) %>%
  mutate(macro = factor(macro, levels = c("Proteins", "Lipids", "Carbohydrates"), labels = c("P", "L", "C")),
         feed = factor(feed, levels = c("reference", "past", "future")),
         total_r = total * 100 %>% round(1),
         digest_r = digest * 100 %>% round(1))
```

Feeds came from [@cottrell_origins_nodate; @cottrell_global_2020].

@@

* The reference feed is `r filter(feed_summary, feed == "reference", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "reference", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "reference", macro == "C")$total_r`% carbohydrate.
* The past feed is `r filter(feed_summary, feed == "past", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "past", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "past", macro == "C")$total_r`% carbohydrate.
* The future feed is `r filter(feed_summary, feed == "future", macro == "P")$total_r`% protein, `r filter(feed_summary, feed == "future", macro == "L")$total_r`% lipid, `r filter(feed_summary, feed == "future", macro == "C")$total_r`% carbohydrate.
* Within the reference feed, protein is overall `r filter(feed_summary, feed == "reference", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "reference", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "reference", macro == "C")$digest_r`% digestible.
* Within the past feed, protein is overall `r filter(feed_summary, feed == "past", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "past", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "past", macro == "C")$digest_r`% digestible.
* Within the future feed, protein is overall `r filter(feed_summary, feed == "future", macro == "P")$digest_r`% digestible, lipid is overall `r filter(feed_summary, feed == "future", macro == "L")$digest_r`% digestible, and carbohydrate is overall `r filter(feed_summary, feed == "future", macro == "C")$digest_r`% digestible.

```{r feed summary ideas}
#| fig-cap: | 
#|   Ideas for how to present the differences between feeds. Top plot shows the protein (red), lipids (yellow) and carbohydrate (blue) composition, with the digestible portion shown darker and the undigestible portion shown lighter. Bottom plot shows the proportion of each feed composed of each types of ingredient.

p1 <- feed_summary %>%
  mutate(digest_total = digest * total) %>% 
  ggplot(aes(x = feed, y = total, fill = macro)) +
  geom_col(position = "dodge", alpha = 0.55, colour = "black") +
  geom_col(mapping = aes(y = digest_total), position = "dodge", alpha = 1, colour = "black") +
  scale_fill_manual(values = macro_pal) +
  scale_y_continuous(breaks = seq(0,0.5,0.1), labels = seq(0,50,10)) +
  scale_x_discrete(labels = c("reference" = "Reference", "past" = "Past", "future" = "Future")) +
  labs(x = "Feed", y = "Proportion (%)") +
  prettyplot()

feed_ings <- rbind(
  feed_params[[1]][[1]] %>% mutate(feed = as.factor("reference")), 
  feed_params[[2]][[1]] %>% mutate(feed = as.factor("past")), 
  feed_params[[3]][[1]] %>% mutate(feed = as.factor("future"))
) %>%
  rename(protein = macro) %>%
  mutate(
    category = case_when(
      str_detect(ingredient, "fish-oil") ~ "fish",
      str_detect(ingredient, "fishmeal") ~ "fish",
      str_detect(ingredient, "krill") ~ "other-marine",
      str_detect(ingredient, "soy") ~ "legume",
      str_detect(ingredient, "pea") ~ "legume",
      str_detect(ingredient, "guar") ~ "legume",
      str_detect(ingredient, "faba") ~ "legume",
      str_detect(ingredient, "corn") ~ "wheat-corn",
      str_detect(ingredient, "wheat") ~ "wheat-corn",
      str_detect(ingredient, "chicken") ~ "chicken",
      str_detect(ingredient, "bacteri") ~ "bact-fungi-micro",
      str_detect(ingredient, "yeast") ~ "bact-fungi-micro",
      str_detect(ingredient, "spirulina") ~ "bact-fungi-micro",
      str_detect(ingredient, "bsf") ~ "insect",
      T ~ "other-plant"
    ) %>% 
      factor(levels = c("fish", "other-marine", "chicken", "wheat-corn", "legume", "other-plant", "insect", "bact-fungi-micro"))
  )

p_ings <- feed_ings %>% 
  mutate(feed = factor(feed, levels = c("reference", "past", "future"), labels = c("Reference", "Past", "Future"))) %>% 
  group_by(feed, category) %>%
  reframe(proportion = sum(proportion)) %>% 
  ggplot(aes(x = "", y = proportion, fill = category)) +
  geom_col(width = 1, colour = "black") +
  coord_polar("y", start = 0) +
  scale_fill_manual(
    name = "Ingredient category",
    values = c("fish" = "royalblue3", "other-marine" = "turquoise2", "chicken" = "hotpink1", "wheat-corn" = "moccasin", "legume" = "forestgreen", "other-plant" = "darkolivegreen1", "insect" = "firebrick3", "bact-fungi-micro" = "darkorange"), 
    labels = c("Fish meal or oil", "Other marine ingredients", "Chicken", "Wheat and corn", "Legumes", "Other plant ingredients", "Insects", "Bacteria, fungi or microalgae")) +
  facet_grid(cols = vars(feed)) +
  theme_void() +
  theme(
    text = element_text(family = "serif", size = 12, colour = "black"),
    legend.position = "bottom",
    strip.text = element_blank(),
    strip.text.x = element_text(size = 14)
  )

plot_grid(p1, p_ings, nrow = 2)
```

@@

```{r raw biomass and weight data}
farmrun_files <- file.path(output_cohort_growth_data_path) %>% 
  list.files(full.names = T)

weight <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["weight_stat"]]}) %>%
  bind_rows()
biomass <- purrr::map(farmrun_files, function(f) {qs::qread(f)[["biomass_stat"]]}) %>%
  bind_rows()
```

@@

@@

uneaten_total <- farmrun_files %>% 
  purrr::map(function(f) {qs::qread(f)[["total_uneat_stat"]]}) %>% 
  bind_rows() %>% 
  merge(biomass, by = c("farm_ID", "feed", "t")) %>% 
  rename(uneat_mean = mean.x, biomass_mean = mean.y,
         uneat_sd = sd.x, biomass_sd = sd.y) %>% 
  mutate(uneat_sd = uneat_sd/uneat_mean,
         biomass_sd = biomass_sd/biomass_mean,
         uneat_biom_mean = uneat_mean/biomass_mean,
         uneat_biom_sd = sqrt(uneat_sd^2+biomass_sd^2)*uneat_biom_mean)
```

```{r uneaten feed analysis}
uneaten_total_stats <- uneaten_total %>% 
  group_by(feed, farm_ID) %>% 
  reframe(total = sum(uneat_biom_mean)) %>% 
  group_by(feed) %>% 
  reframe(min = minna(total),
          max = maxna(total),
          mean = meanna(total)) %>% 
  mutate(min = min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         max = max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1"),
         mean = mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1")) %>% 
  mutate(min = round(min,2),
         max = round(max,2),
         mean = round(mean,2))

uneaten_total_compare <- uneaten_total %>% 
  group_by(feed, farm_ID) %>% 
  reframe(total = sum(uneat_biom_mean)) %>% 
  pivot_wider(names_from = "feed", values_from = "total", id_cols = "farm_ID") %>% 
  mutate(diff_past = past-reference,
         diff_future = future-reference,
         diffperc_past = diff_past/reference,
         diffperc_future = diff_future/reference) %>% 
  dplyr::select(-c(reference, future, past)) %>% 
  pivot_longer(names_to = c("measure", "feed"), names_sep = "_", values_to = "value",
               cols = contains("diff"), names_transform = list(measure = as.factor, feed = as.factor)) %>% 
  group_by(feed, measure) %>% 
  reframe(min = minna(value),
          max = maxna(value),
          mean = meanna(value)) %>% 
  mutate(
    min = case_when(measure == "diffperc" ~ 100*min,
                    T ~ min %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
    max = case_when(measure == "diffperc" ~ 100*max,
                    T ~ max %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
    mean = case_when(measure == "diffperc" ~ 100*mean,
                     T ~ mean %>% set_units("g g_fish-1") %>% set_units("g kg_fish-1") %>% drop_units()),
    )
```

Total uneaten feed across a cohort (548 days) fed the reference feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "reference"]` to 
`r uneaten_total_stats$max[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish, with a mean of 
`r uneaten_total_stats$mean[uneaten_total_stats$feed == "reference"]` g kg$^{-1}$ fish.

* Differences between the feeds were very small, with the past scenario producing 
* but slightly less uneaten feed was lost in the reference scenario. Uneaten past feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "past"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "past"]`) while uneaten future feed ranged from 
`r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` to `r uneaten_total_stats$min[uneaten_total_stats$feed == "future"]` g kg$^{-1}$ (mean of `r uneaten_total_stats$mean[uneaten_total_stats$feed == "future"]`).
* @fig-total-uneaten-perday shows the range of total uneaten feed per day across countries.
